onsetsync demo

### 2022-11-10 README.Rmd
Updated readme to include links to notebooks

@@

For more examples, see [Get started](docs/articles/onsetsync.html).

>>>>

For trying the package with notebooks, jump to <A HREF="#more">more information</A>.

@@

## More information
<a id="more">

For more examples, see [Get started](https://tuomaseerola.github.io/onsetsync/articles/onsetsync.html) or see the [function reference](https://tuomaseerola.github.io/onsetsync/reference/index.html).

- [Tutorial as a Rmarkdown notebook](https://github.com/tuomaseerola/onsetsync/blob/master/onsetsync.Rmd) which requires you to run the code in RStudio.

- [Tutorial as a Jupyter notebook](https://github.com/tuomaseerola/onsetsync/blob/master/onsetsync.ipynb) which allows you to run the code in Colab (in your browser).
